Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-28 paper/ms.tex
Add some masses of clusters to table

\begin{deluxetable*}{cccccc}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 \\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 \\
NGC2451 & 193.7 & 5.8 & -1805 & 0.21 & 73.4 \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9
\enddata
\tablerefs{\citet{2018AA...616A..10G}}
\label{tab:real_clusters}
\end{deluxetable*}

>>>>

\begin{deluxetable*}{ccccccc}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within $250\,\pc$ of the Sun.}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} \\ \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$}}f
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 & 352\tablenotemark{a} \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 & 410\tablenotemark{b} \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 &  \\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 & 400\tablenotemark{d} \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 & \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 & \\
NGC2451 & 193.7 & 5.8 & -1805 & 0.21 & 73.4 & \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 & \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9 & 
\enddata

\tablenotetext{a}{\citet{2016MNRAS.457.1028S}}
\tablenotetext{b}{\citet{2007AA...471..499M}}
\tablenotetext{c}{}
\tablenotetext{d}{\citet{1998AA...331...81P}}

\tablerefs{\citet{2018AA...616A..10G}}
\label{tab:real_clusters}
\end{deluxetable*}
